### 2018-01-09 submission/supplemental.Rmd
change table orders

**Table S1: Alpha Diversity Metrics RR in Tissue for Adenoma**

@@

@@

**Table S2: Alpha Diversity Metrics RR in Tissue for Unmatched Carcinoma Non-Carcinoma Samples**

@@

**Table S3: Alpha Diversity Metrics RR in Tissue for Matched Carcinoma Non-Carcinoma Samples**

@@

**Table S4: Bray-Curtis Distance Matrix Analyzed by PERMANOVA for Stool Adenoma**

table_s4 <- temp_t1 %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = stringr::str_replace(study, 
                                      c("brim", "zeller", "baxter", "hale"), 
                                      c("Brim", "Zeller", "Baxter", "Hale")))

colnames(table_s4) <- c("F statistic", "R2", "P-value", "Study", "Adenoma (n)", "Control (n)")

kable(table_s4, format = "markdown", align = 'c', padding = 2)
```

**Table S5: Bray-Curtis Distance Matrix Analyzed by PERMANOVA for Stool Carcinoma**

table_s5 <- temp_t2 %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = stringr::str_replace(study, 
                                      c("wang", "weir", "ahn", "zeller", "baxter", "hale", "flemer"), 
                                      c("Wang", "Weir", "Ahn", "Zeller", "Baxter", "Hale", "Flemer")))

colnames(table_s5) <- c("F statistic", "R2", "P-value", "Study", "Carcinoma (n)", "Control (n)")

kable(table_s5, format = "markdown", align = 'c', padding = 2)
```

>>>>

**Table S1: Bray-Curtis Distance Matrix Analyzed by PERMANOVA for Stool Adenoma**

@@

table_s1 <- temp_t1 %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = stringr::str_replace(study, 
                                      c("brim", "zeller", "baxter", "hale"), 
                                      c("Brim", "Zeller", "Baxter", "Hale")))

colnames(table_s1) <- c("F statistic", "R2", "P-value", "Study", "Adenoma (n)", "Control (n)")

kable(table_s1, format = "markdown", align = 'c', padding = 2)
```

**Table S2: Bray-Curtis Distance Matrix Analyzed by PERMANOVA for Stool Carcinoma**

table_s2 <- temp_t2 %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = stringr::str_replace(study, 
                                      c("wang", "weir", "ahn", "zeller", "baxter", "hale", "flemer"), 
                                      c("Wang", "Weir", "Ahn", "Zeller", "Baxter", "Hale", "Flemer")))

colnames(table_s2) <- c("F statistic", "R2", "P-value", "Study", "Carcinoma (n)", "Control (n)")

kable(table_s2, format = "markdown", align = 'c', padding = 2)
```

**Table S3: Alpha Diversity Metrics RR in Tissue for Adenoma**

@@

**Table S4: Alpha Diversity Metrics RR in Tissue for Unmatched Carcinoma Non-Carcinoma Samples**

@@

**Table S5: Alpha Diversity Metrics RR in Tissue for Matched Carcinoma Non-Carcinoma Samples**

@@
